A Fast kNN Algorithm Using Multiple Space-Filling Curves

### 2022-05-05 2022/Sensors/kNN.tex
add one more paper
add response to comment 1 of reviewer 1

%%%% ДЛЯ РУССКОГО ТЕКСТА закомментировать потом!
%\usepackage{inputenc}
%\usepackage[T2A,T1]{fontenc}
%\usepackage[english,russian]{babel}
%\usepackage{cmap}
%%%%

@@

Here is a more detailed description of these algorithms.
\\[12pt]
\textit{Data preparation}
\\[12pt]
To run Algorithms A and B, we need to compute the preimages $\{x_i^0, x_i^1, ..., x_i^L\}$ on one-dimensional scales for all objects $\omega_i$, and order them in ascending order. It is convenient to use RB-tree-based data structures to store ordered one-dimensional values. The number of instances of tree structures is equal to the number of scales.

>>>>

%%% ДЛЯ РУССКОГО ТЕКСТА закомментировать потом!
\usepackage{inputenc}
\usepackage[T2A,T1]{fontenc}
\usepackage[english,russian]{babel}
\usepackage{cmap}
%%%

@@

Here is a more detailed description of these algorithms.
\\[12pt]
\textit{Data preparation}
\\[12pt]
To run Algorithms A and B, we need to compute the preimages $\{x_i^0, x_i^1, ..., x_i^L\}$ on one-dimensional scales for all objects $\omega_i$, and order them in ascending order. It is convenient to use RB-tree-based data structures to store ordered one-dimensional values, <Сысоев>алгоритмическая сложность операции поиска в котором имеет оценку O(logN). В качестве реализации RB-tree мы использовали контейнер set из стандартной библиотеки языка С++. <Сысоев> The number of instances of tree structures is equal to the number of scales.
